### 2025-04-12 source/cadabra/checks/check-genGamma.tex
Simplified installation, updated hybrid-latex tools
1. Non-trivial refactoring of the build/install scripts.
   This was both to tidy the file structure as well as to simplify the installation
   process. The default install is now as simple as "source SETPATHS; make install".
   Almost all install/build/test/clean actions are now controlled by Makefiles.

2. Updated cdbpreproc.py.
   The Cadabra preprocessor will strip any in-line comments (such as cdb tags) from
   what it thinks are short lines. This failed for some of the examples (some in line
   comments were not deleted). This was fixed

@@

This code was written as a check for the {\tt genGamma.tex} code. I had a discrepency between my
newly created Cadabra v2.0 codes and my old Cadabra v1.0 codes (which were the basis of my lcb09-03 paper).
I found that my new codes agreed with this code and thus my old codes were wrong. I found the errors
in the old code (see the updated codes in v1.0/rnc-new/gen-gamma.cdbp, see also the file v1.0/rnc-new/NOTES.txt).

>>>>

\def\Date{18 May 2024}
% \def\FileID{file:}

@@

This code was written as a check for the {\tt genGamma.tex} code. I had a discrepency between my
newly created Cadabra v2.0 codes and my old Cadabra v1.0 codes (which were the basis of my
lcb09-03 paper). I found that my new v2.0 codes agreed with this code and thus my old v1.0 codes
were wrong. I found the errors in the old code but it seems that (at some time) I deletd the
details of those errors. I have no idea why I did that -- clearly another mistake on my part.
What I do recall is that there were two errors, 1) I had declared {\tt
\nabla{#}::PartialDerivative} and 2) In some crucial part of the generalised gamma computation
the Cadabra {\tt asym} algorithm did not correctly do the full anti-symmetrisation. The first
mistake is really a stupid mistake on my part -- it forces $\nabla_{ab} = \nabla_{ba}$. So all
second and higher order derivatives of $R_{abcd}$ are wrong. This means that the expressions (in
my v1.0 results) that depend upon the generalised gammas (e.g., the geodesic bvp, ivp and Lsq's)
are wrong (from the second oder terms and above, yikes). The seond problem, to do with incomplete
and incorrect anti-symmetrisations, was a Cadabra problem. The new v2.0 codes fixes these problem.

### 2025-04-12 source/cadabra/detg2.tex
Minor housekeeping. No major changes.
Fixed a few typos in some of the tex and sh files.
Simplified installation, updated hybrid-latex tools
1. Non-trivial refactoring of the build/install scripts.
   This was both to tidy the file structure as well as to simplify the installation
   process. The default install is now as simple as "source SETPATHS; make install".
   Almost all install/build/test/clean actions are now controlled by Makefiles.

2. Updated cdbpreproc.py.
   The Cadabra preprocessor will strip any in-line comments (such as cdb tags) from
   what it thinks are short lines. This fa

{\bf Note that Calzetta uses an opposite sign for $R_{abcd}$ so when comparing my results
against Calzetta do take note of this flipped sign in $R_{abcd}$.}

@@

   # the following are based on sqrt-Ndetg.tex

>>>>

{\bf Note} that Calzetta etal. use an opposite sign for $R_{abcd}$ so when comparing the
following results against Calzetta do take note of this flipped sign in $R_{abcd}$.

@@

   # the following are based on sqrt-detg.tex

### 2025-04-12 source/cadabra/sqrt-detg.tex
Removed dependancy on cadabra2python
I used cadabra2python as a backdoor way to import .cdb files.
This would create a .py file which would then be imported using
a standard Python import statement.

But Cadabra can now (since at least version 2.5.x) import .cdb files directly.
So I no longer need the backdoor hack.

\documentclass[12pt]{pylatex}

@@

Expand $\sqrt{g}$ in powers of $R,\nabla R$ etc.

@@

@@

@@

@@

>>>>

\def\Date{19 Jan 2024}
% \def\FileID{file:}

\documentclass[12pt]{pylatex}
\usepackage{config}

@@

% =================================================================================================
\section*{Side calculations for detg2.tex}

This is a short computation for the expansions of $\sqrt{-\det g(x)}$ and $\log\left(-\det g(x)\right)$
in powers of $R$ and its derivatives. The results wil be used in {\tts detg2.tex}.

The starting point is to write $\det g(x)$ in the form
\begin{dgroup*}
   \begin{dmath*} -g(x) = 1 + a \epsilon^2 + b \epsilon^3 + c \epsilon^4 + d \epsilon^5 + \BigO{\epsilon^6} \end{dmath*}
\end{dgroup*}
where $\eps$ is introduced as an expansion parameter and where $a,b,c$ and $d$
are simple expressions in $R$ and its derivatives. These can be read off directly
from the expansion for $\det g(x)$ given in {\tts detg2.tex}.

\clearpage

@@

   det = 1 + eps**2*a + eps**3*b + eps**4*c + eps**5*d   # py (det.001,det)
   # this foo will be used in detg2.tex
   foo = Rational(1,2) + det/2 - (eps**4*a**2)/8 - (eps**5*a*b)/4   # py (foo.001,foo)
   err = simplify (ans-foo)   # py (err.001,err)

@@

\begin{dgroup*}
   \begin{dmath*} \py*{det.001} \end{dmath*}
   \begin{dmath*} \py*{foo.001} \end{dmath*}
   \begin{dmath*} \py*{err.001} \end{dmath*}
\end{dgroup*}

\clearpage

@@

   det = 1 + eps**2*a + eps**3*b + eps**4*c + eps**5*d   # py (det.001,det)
   # this foo will be used in detg2.tex
   foo = -1 + det - (eps**4*a**2)/2 - (eps**5*a*b)       # py (foo.002,foo)
   err = simplify (ans-foo)   # py (err.002,err)
\end{python}

@@

\begin{dgroup*}
   \begin{dmath*} \py*{det.001} \end{dmath*}
   \begin{dmath*} \py*{foo.002} \end{dmath*}
   \begin{dmath*} \py*{err.002} \end{dmath*}
\end{dgroup*}
